%----------------------------------------------------------------------------------------
%	PERSONALIZED CV - SIMON RENUART
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv}
\usepackage{enumitem}
\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth}
	\vspace{-\baselineskip}
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Simon}}}}}
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Renuart}}}}}
	\newline
    \newline
    \vspace{6pt}
	{\huge AI Software Engineer}
\end{minipage}
\hfill
\begin{minipage}[t]{\textwidth}
    \vspace{-\baselineskip}
    \icon{MapMarker}{12}{Melbourne, Aus}\\
    \icon{At}{12}{\href{mailto:Simon.renuart.pro@outlook.com}{Simon.renuart.pro@outlook.com}}\\
    \icon{Linkedin}{12}{\href{https://linkedin.com/in/simonrenuart}{/simonrenuart}}\\
    \icon{Github}{12}{\href{https://github.com/sire6/}{/sire6}}\\
    \icon{Globe}{12}{\href{https://simonrenu.ddns.net/}{https://simonrenu.ddns.net/}}\\
\end{minipage}


%----------------------------------------------------------------------------------------
%	SUMMARY AND SKILLS
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
% SUMMARY ET SKILLS COTE A COTE
%----------------------------------------------------------------------------------------

\vspace{-0.5em}
\begin{minipage}[t]{0.40\textwidth}  % 48% largeur pour Summary

  \cvsect{Summary}
  \vspace{-\baselineskip}
  \newline

AI Software Engineer with over 3 years of experience in designing, implementing, scaling, and deploying AI computer vision solutions. Proficient in the Nvidia AI stack with experience with Apache Kafka and Flink. Passionate about tackling challenging projects that push boundaries and require continuous learning of the latest innovations and technologies. A genuine team player dedicated to fostering collaboration through effective communication and knowledge sharing.
\end{minipage}
\hfill
\begin{minipage}[t]{0.57\textwidth}  % Largeur Skills
  \cvsect{Skills}
  \vspace{-\baselineskip}
  \vspace{1em}

  \begin{minipage}[t]{0.25\textwidth}  % Programming 25%
    \textbf{Programming}
    \begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
      \item Python
      \item C++
      \item Bash
      \item Java
      \item SQL
      \item HTML/CSS
    \end{itemize}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.72\textwidth}  % Technologies and Tools 72% (un peu moins que 75% pour marge)
    \textbf{Technologies and Tools}
    
    \begin{minipage}[t]{0.48\textwidth}  % 48% première colonne
      \begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
        \item Docker
        \item Linux
        \item Apache Flink
        \item Apache Kafka
        \item FFMPEG
        \item GStreamer
        \item Tensorflow
        \item PyTorch
        \item Darknet (YOLO)
        \item Azure Pipelines
        \item Github Actions
      \end{itemize}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.48\textwidth}  % 48% deuxième colonne
      \begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
        \item Nvidia AI stack
          \begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
            \item Jetson platforms
            \item Deepstream
            \item TensorRT
            \item TAO Toolkit
            \item Model Analyzer
            \item Dynamo-Triton 
          \end{itemize}
        \item IP/CSI cameras
        \item Sensors
        \item Nginx
        \item OSS self-hosting
      \end{itemize}
    \end{minipage}
  \end{minipage}
\end{minipage}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{}
    {Computer Vision Software Engineer \textnormal{- TRU Recognition, Melbourne (Australia)}}
		{Nov 2023 -- Present}
    {
      \vspace{-1em}
      \begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
        \item Lead the design, implementation and deployment of real-time computer vision solutions using the Nvidia AI stack for cloud and on-premises environments (200+ cameras) in retail and security sectors.
        \item Optimise throughput, latency and accuracy of computer vision solutions to ensure peak performance on Nvidia L4 and A10 GPUs.
        \item Process thousands of events per second via Apache Kafka and Apache Flink, transforming and aggregating sensor data into actionable insights.
        \item Establish and maintain data-driven metrics to evaluate models and multi-object tracking systems for production readiness.
      \end{itemize}
    }
  \entry
		{}
		{Computer Vision Software Engineer \textnormal{- Phoenix AI, Peruwelz (Belgium)}}
		{Sep 2021 -- Jan 2023}
    {
      \vspace{-1em}
      \begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
        \item Developed and deployed real-time computer vision solutions using the Nvidia AI stack for Nvidia Jetson platforms.
        \item Established processes to build image datasets, train models and continuously improve solution performance.
        \item Integrated Jetson-based systems with in-country cloud platforms (UK, Belgium, France) to transmit real-time events over cellular networks while ensuring data sovereignty.
        \item Managed Nvidia Jetson setup, including OS and library installation (Nvidia JetPack), bootloader configuration and integration of peripherals such as IP cameras, GPS, mobile data and voltage sensors.
      \end{itemize}
    }	
  \entry
		{}
		{Computer Vision Software Engineer Intern \textnormal{- Infrabel, Brussels (Belgium)}}
		{Jul 2020 -- Sep 2020}
    {
      \vspace{-1em}
      \begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
        \item Developed OpenCV-based computer vision algorithms to monitor countersink tolerances for industrial defect detection.
        \item Built image datasets and trained deep learning models to detect defects on manufactured concrete surfaces.
      \end{itemize}
    }
\end{entrylist}



%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\vspace{-1em}
\cvsect{Education}

\begin{entrylist}
	\entry
		{}
		{Master's degree, Computer Engineering and Management}
		{2019 -- 2021}
		{UMONS Faculty of Engineering (FPMS) \newline Specialization: Artificial Intelligence and Decision Aid \newline Grade: Great Distinction}
	\entry
		{}
		{Bachelor's degree, Applied Sciences Engineering}
		{2015 -- 2019}
		{UMONS Faculty of Engineering (FPMS)}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\vspace{-1em}
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}
    \cvsect{Languages}
    
    \textbf{French} - Native\\
	  \textbf{English} - Professional\\
	  \textbf{Dutch} - Intermediate
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
    \vspace{-\baselineskip}
    \cvsect{Interests}

    \begin{itemize}[noitemsep, topsep=0pt, leftmargin=*]
      \item \textbf{Efficient computing}
      \item \textbf{Creative problem solving}
      \item \textbf{AI}
      \item \textbf{Cooking}
      \item \textbf{Surfing}
    \end{itemize}
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}
    \cvsect{Other}
    
	\textbf{Driving license} - Yes\\
	\textbf{Nationality} - Belgian\\
  \textbf{Valid 482 visa} - Yes
\end{minipage}

\end{document}
